File-based localization of numerical perturbations in data analysis pipelines

### 2020-03-29 paper.tex
Added a comment in methods

\toolname identifies the processes in a pipeline that produce different results in two different conditions.  
In Condition 1, a directed, rooted, bipartite provenance graph is recorded for
each subject, where nodes represent application processes and files, and
edges represent read and write file accesses (Step 1 in Figure~\ref{fig:overview-tool}).
\emph{Transient} files are then identified as
 files that are either deleted during the execution, or modified by
multiple processes (Step 2). \toolname re-runs the pipeline to save these files
right after they are produced, resulting in a provenance \emph{DAG}
(Directed Acyclic Graph) in which file nodes have a single parent (in-degree
of 1) (Step 3). This DAG is then compared to the one produced from
Condition 2, in a step-by-step execution to prevent the propagation of differences (step 4).
\toolname finally produces a labeled graph that identifies the
non-reproducible processes of the pipeline.

>>>>

\toolname identifies the processes in a pipeline that produce different results when executed in two different conditions.  
In Condition 1, a directed, rooted, bipartite provenance graph is recorded for
each subject, where nodes represent application processes and files, and
edges represent read and write file accesses (Step 1 in Figure~\ref{fig:overview-tool}).
\emph{Transient} files are then identified as
 files that are either deleted during the execution, or modified by
multiple processes (Step 2). \toolname re-runs the pipeline to save these files
right after they are produced, resulting in a provenance \emph{DAG}
(Directed Acyclic Graph) in which file nodes have a single parent (in-degree
of 1) (Step 3) \tristan{Ali, this is not true in Figure 1: at step 3 there are still transient files}. This DAG is then compared to the one produced from
Condition 2, in a step-by-step execution to prevent the propagation of differences (step 4).
\toolname finally produces a labeled graph that identifies the
non-reproducible processes of the pipeline.
